---
title: "Exercises - Linear regression"
output:
  html_document:
    code_download: true
mathjax: local
---

## Lecture revision
### Main points to remember from the lecture

* Simple linear regression is about looking for an association between a response (y-variable) and a predictor (x-variable).
*  How do I test assumptions in linear regression?
*  Two-sample t-test is just a special case of simple linear regression!

### Code we learned

First call libraries
```{r message=FALSE, warning=FALSE, paged.print=TRUE}
library(tidyverse)
knitr::opts_chunk$set(fig.path='Figs/')
```

Linear model with `quality` as response, and `catchment` as predictor using dataset `data_qual`
```{r}
data_qual <- read_csv(file = "data/waterQual.csv")
mod_qual1<-lm(quality~catchment, data = data_qual)
summary(mod_qual1)
```

Confidence interval for coefficient of catchment (and intercept)
```{r}
confint(mod_qual1)
```


## Questions

Remove all object from the environment before we start.
```{r}
rm(list = ls())
```


### Question 1
**Consider the guinea pigs (smoking) example again: **

*Is there an association between the number of errors and treatment group (Control and Nicotine)?*

**a) Load the `smokePregnant` data into R.**
```{r}

```

**b) The data could be organised differently. Instead of looking like this.**

| Treatment | Control  |
|-----------|----------|
|     38    |    11    |
|     26    |    19    |
|     33    |    15    |
|     89    |    47    |
 [etc]                                

**Can you make it look like this:**

| errors | treatment |
|--------|-----------|
| 38     | Nicotine  |
| 26     | Nicotine  |
| 33     | Nicotine  |
| 89     | Nicotine  |
| [etc]  |           |
| 11     | Control   |
| 19     | Control   |
| 15     | Control   |
| 47     | Control   |
| [etc]  |

```{r}

```

**c) Left-skewed, right-skewed, symmetric? If you think `errors` needs transforming...**
```{r}

```


**d) In the session 1 exercises, we used a two-sample t-test. Let's now use linear regression. To do this:**

* Construct a new variable `numericTreatment`, which takes the value 1 for `Nicotine` and 0 for `Control`.
* Fit a linear regression for errors (transformed if required) against `numericTreatment`.
* Compare the output to that obtained previously for the two-sample t-test.
```{r}

```

**e) What did you assume in the linear regression model above?  What could have been done to ensure assumptions were reasonable?**


```{r}

```


### Question 2

**Consider the water quality example:**

*How is water quality in creeks associated with/related to the size of the catchment area?*

**a) Load the `waterQual` data into R.**
```{r}

```

**b) What is the research question? Descriptive statistics or inference? Do we have a specific hypothesis to test or are we just estimating some parameter?**



**c) What are the main properties of the data? One variable or two? Categorical or quantitative?**



**d) Produce a graph relevant to the original research question.**
```{r}

```

**e) What model do we want to use here? What parameter in this model describes how water quality is associated with catchment area?**

```{r}

```

**f) What is a plausible range of values for this key parameter? Hint: Use `?confint`**
```{r}

```

**g) What did you assume in the above?  What could have been done to ensure assumptions were reasonable?**
```{r}

```
 
